Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms

### 2019-06-02 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/presentation.tex
Full initial version of the presentation was done.

>>>>

\begin{frame}
\frametitle{Individuals Representation}
\begin{itemize}
  \item Formal grammar sentences with variable length
  \item Each of the operations can appear at any position many times
  \item The average expected length of the chromosomes is between 50 and 100
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Recombination Parameters}
\begin{itemize}
  \item Single cut point crossover
  \item Random change of a single instruction mutation
  \item Random selection of parents
  \item Elitism rule
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Fitness Value}
\begin{itemize}
  \item Instructions from GA individual are applied over the scrambled cube
  \item Hausdorff distance between manipulated cube and solved cube is calculated
  \item Lower fitness values are for better individuals
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Proposed Fitness Evaluation}
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth,height=0.65\textwidth]{fig01}
  \label{fig01}
\end{figure}
\end{frame}

\section{Experiments and Results}

\begin{frame}
\center \huge{Experiments and Results}
\end{frame}

\begin{frame}
\frametitle{Platform Setup}
\begin{itemize}
  \item Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM
  \item Mac OS X 10.13.6
  \item Apple LLVM version 9.1.0 / Open MPI
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Genetic Algorithm Parameters}
\begin{itemize}
  \item Generation gap: 0.93
  \item Crossover rate: 0.98
  \item Mutation rate: 0.01
  \item Maximum generations: 10000
  \item Number of individuals: 37
  \item Number of variables: floating
  \item Inserted rate: 100
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Star Topology Results}
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth,height=0.5\textwidth]{fig03}
  \label{fig03}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Incident Nodes Participation}
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth,height=0.5\textwidth]{fig04}
  \label{fig04}
\end{figure}
\end{frame}
